---
title: "Lab 1 Team 28"
output: html_notebook
---
The code below demonstrate our the ability to collect, work with,
and clean a data set. 

The first step is to read data.
```{r}
test_data <- read.table("Desktop/Lab_1_data/test/X_test.txt")
train_data <- read.table("Desktop/Lab_1_data/train/X_train.txt")
```
In the second step we are merging the training data and the testing data. And print out the output below.
```{r}
combined_data <- rbind(train_data, test_data)
combined_data
```
Third, we label the dataset created in step 1 with a descriptive variable (column names from the Features.txt file).
```{r}
features <- read.table("Desktop/Lab_1_data/features.txt")
colnames(combined_data) <- features$V2
features
```
Fourth, we extract only the measurements (columns) on the mean and standard deviation
for each measurement from the data set created on step 1
```{r}
selected_columns <- grep("mean\\(\\)|std\\(\\)", features$V2)
selected_data <- combined_data[, selected_columns]
selected_data
```
Next, we merge the training labels data set and the testing labels data set.
```{r}
train_labels <- read.table("Desktop/Lab_1_data/train/y_train.txt")
test_labels <- read.table("Desktop/Lab_1_data/test/y_test.txt")
combined_labels <- rbind(train_labels, test_labels)
combined_labels
```
Lastly, we use descriptive activity names to name the activities in the data set created in
step 4 and merged the data set created in step 3 and the data
set created in step 4.
```{r}
activity_labels <- c("WALKING", "WALKING_UPSTAIRS", "WALKING_DOWNSTAIRS", "SITTING", "STANDING", "LAYING")
combined_labels$V1 <- factor(combined_labels$V1, levels = 1:6, labels = activity_labels)
final_data <- cbind(selected_data, Activity = combined_labels$V1)
final_data
```


